Defficiency Screen Functional Analysis

### 2023-07-10 DeficiencyScreen/KEGG_Analysis.Rmd
update

```{r setup, include=FALSE}
library(rgl)
knitr::opts_chunk$set(echo = FALSE, fig.align="center")
knitr::knit_hooks$set(webgl = hook_webgl)
```

```{r echo = F, include=F}
##Load Libraries

library(biomaRt)
library(org.Dm.eg.db)
library(goseq)
library(GO.db)
library(visNetwork)
library(rrvgo)
library(plotly)
library(KEGGREST)
library(pathview)
##library(RColorBrewer)
```

```{r echo = F, include =F}
##load all files from github
GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)

Df.data = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/DeficiencyModifierGenes.csv", row.names = 1)
Df.data$CG = GeneIDKey[row.names(Df.data),"CG"]

kegg = readRDS("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/kegg.symbol2path.RData")

keggID=keggConv("dme","ncbi-geneid")

kegg.names = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv", row.names = 1)

Moderate.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/ModerateKEGGAnalysis.csv", row.names = 1)

Strong.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/StrongKEGGAnalysis.csv", row.names = 1)

Repress.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorKEGGAnalysis.csv", row.names = 1)

Lethal.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalKEGGAnalysis.csv", row.names = 1)

Enhance.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerKEGGAnalysis.csv", row.names = 1)

@@

ShowKEGG = function(PathwayID){
download.kegg(pathway.id= PathwayID, species = "dme")
xml.file=paste0("dme",PathwayID,".xml")
node.data=node.info(xml.file)

@@

pv.pars= keggview.native(plot.data.gene=plot.data.gene,
                         cols.ts.gene=cols.ts.gene, 
                         node.data=node.data,
                         pathway.name=paste0("dme", PathwayID),
                         same.layer=T, plot.col.key=F, out.suffix = kegg.names[paste0("dme", PathwayID),1])

@@

data = Moderate.KEGG

@@

```{r echo = F, include = F}
PathwayID = "04150"

@@

```{r}
knitr::include_graphics(paste0("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/dme",PathwayID, ".", kegg.names[paste0("dme", PathwayID),1], ".png"))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F, include=F}
##Load Libraries
library(plotly)
library(pathview)
```

```{r echo = F, include =F}
##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
GeneIDKey = read.csv(paste0(git.dir,"GeneralDataFiles/GeneIDKey.csv"),row.names = 1)
Df.data = read.csv(paste0(git.dir,"GeneralDataFiles/DeficiencyModifierGenes.csv"),row.names = 1)
Df.data$CG = GeneIDKey[row.names(Df.data),"CG"]
Df.data$Repress = 0
Df.data$Repress[Df.data$Moderate == 1|Df.data$Strong == 1] = 1
kegg = readRDS(gzcon(url(paste0(git.dir,"DeficiencyScreen/DataFiles/kegg.symbol2path.RData"))))
kegg.names = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/KEGG.names.csv"), row.names = 1)

Moderate.KEGG = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/ModerateKEGGAnalysis.csv"), row.names = 1)
Strong.KEGG = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/StrongKEGGAnalysis.csv"), row.names = 1)
Repress.KEGG = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/RepressorKEGGAnalysis.csv"), row.names = 1)
Lethal.KEGG = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/LethalKEGGAnalysis.csv"), row.names = 1)
Enhancer.KEGG = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/EnhancerKEGGAnalysis.csv"), row.names = 1)

@@

if(intersect(list.files(), "KEGG_Image_Files") != "KEGG_Image_Files"){
  dir.create(paste0(dirname(rstudioapi::getSourceEditorContext()$path), "/KEGG_Image_Files/"))
}

Home = dirname(rstudioapi::getSourceEditorContext()$path)
OutputDir = paste0(Home, "/KEGG_Image_Files/")

ShowKEGG = function(PathwayID){

download.kegg(pathway.id= PathwayID, species = "dme", kegg.dir = OutputDir)
xml.file=paste0(OutputDir, "dme",PathwayID,".xml")
node.data=node.info(xml.file)

@@

setwd(OutputDir)
pv.pars= keggview.native(plot.data.gene=plot.data.gene,
                         cols.ts.gene=cols.ts.gene, 
                         node.data=node.data,
                         pathway.name=paste0("dme", PathwayID),
                         same.layer=T, plot.col.key=F, out.suffix = kegg.names[paste0("dme", PathwayID),1],
                         kegg.dir = OutputDir)
setwd(Home)
}

@@

##Options: Moderate.KEGG, Strong.KEGG, Repress.KEGG, Lethal.KEGG, Enhancer.KEGG
data = Repress.KEGG

@@

```{r echo = F, include = F}

PathwayID = "04141"

@@

```{r echo = F}

knitr::include_graphics(paste0(OutputDir, "dme",PathwayID, ".", kegg.names[paste0("dme", PathwayID),1], ".png"))

```{r include = F, echo = F}

GenesInKEGG = Df.data[Df.data$Symbol %in% names(kegg[grep(PathwayID, kegg)]),]
write.csv(GenesInKEGG, paste0(OutputDir,"GenesInKEGG_dme", PathwayID,".csv"))
